---
title: "bjl21500-s_place"
author: "Briana Lettsome"
date: "October 31, 2018"
output: html_document
---

```{r}
library(tidyverse)
library(httr)
library(jsonlite)

get_all_inspections = function(url) {
  
  all_inspections = vector("list", length = 0)
  
  loop_index = 1
  chunk_size = 50000
  DO_NEXT = TRUE
  
  while (DO_NEXT) {
    message("Getting data, page ", loop_index)
    
    all_inspections[[loop_index]] = 
      GET(url,
          query = list(`$order` = "zipcode",
                       `$limit` = chunk_size,
                       `$offset` = as.integer((loop_index - 1) * chunk_size)
                       )
          ) %>%
      content("text") %>%
      fromJSON() %>%
      as_tibble()
    
    DO_NEXT = dim(all_inspections[[loop_index]])[1] == chunk_size
    loop_index = loop_index + 1
  }
  
  all_inspections
  
}

url = "https://data.cityofnewyork.us/resource/9w7m-hzhe.json"

nyc_inspections = get_all_inspections(url) %>%
  bind_rows() 
```

```{r}
nyc_restaurants = nyc_inspections %>%
  janitor::clean_names() %>%
  select(boro, cuisine_description, grade, street, score) %>%
  filter(boro != "Missing")
```


# Graph 1
```{r}
nyc_grades = nyc_restaurants %>%
  select(boro, grade) %>%
  filter(grade %in% c("A", "B"), boro != "Missing") 


nyc_grades %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar()
```

# Graph #2
```{r}
nyc_scores = nyc_restaurants %>%
  select(score, grade, boro) %>%
  filter(grade %in% c("A", "B", "C")) %>%
  group_by(boro) %>%
  summarize(n = n())
```

common_neighborhoods =
  nyc_airbnb %>% 
  count(neighbourhood, sort = TRUE) %>% 
  top_n(2000) %>% 
  select(neighbourhood)

nyc_scores %>%
   ggplot(aes(x = boro, y = score, fill = grade)) +
  geom_boxplot() +
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


ggplot(nyc_scores, aes(x = boro, y = n)) + 
  geom_violin(aes(fill = boro), color = "blue", alpha = .5) + 
  stat_summary(fun.y = median, geom = "point", color = "blue", size = 4)

ggplot(nyc_scores, aes(x = score)) + 
  geom_histogram()
